Graph Generators for Data Science: A Survey

### 2018-06-06 introduction.tex
More paragraphs in the introduction

In this survey we ... \TODO{We consider graph generation targeting multiple subfields, such as graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities}

... \TODO{Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.}

... \TODO{We argue that this classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.}

... \TODO{This survey provides a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks. Finally, we discuss open challenges and missing features of graph generators in view of the evolution of data science.}

>>>>

In this survey we provide a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks. Our aim is to cover a wide range of currently popular areas of graph data processing. In particular, we consider graph generation in the areas of graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities. Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators. The reasons for this scope and classification are as follows:

\begin{enumerate}
  \item Despite the differences of the covered areas, the requirements for the graph data generators can be similar in particular cases. Reusing or learning from tools in other fields can thus bring new opportunities for both researchers and practitioners. 
  \item The selected classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.
\end{enumerate}

To conclude the comparative study, we discuss open challenges and missing features of graph generators in view of the evolution of data science.
